Foregrounds in Fourier Space for Redshifted 21~cm Observatories

### 2015-02-03 ms.tex
Create branch alternate-version, change title
from 13ccbd7:
============

(*) Create a git branch alternate-version

In ms.tex,

(*) Change  title and short title
Modify abstract for alternate version
from ea7f9f8:
============

In ms.tex,

(*) Modify abstract for alternate version

\shorttitle{Dissection of foregrounds in EoR H{\sc i} power spectra}
\shortauthors{Thyagarajan et~al.}

@@

%% \title{Detecting Epoch of Reionization in redshifted 21~cm: contamination in EoR window}
%% \title{Limits on the detection of the Epoch of Reionization from MWA observations of the redshifted 21~cm line}
\title{A Dissection of Foregrounds in Epoch of Reionization Observations from the Murchison Widefield Array}

@@

Detection of 21~cm emission of H{\sc i} from the epoch of reionization, at redshifts $z>6$, is limited primarily by foreground emission.  We investigate the chromatic signatures of an all--sky foreground model imprinted by an instrumental transfer function. Using the delay spectrum technique {\bf that maps the measurements to foreground object locations through signal delays between antenna pairs}, we demonstrate that the foreground signatures that have the largest impact on the H{\sc i} signal arise from power received far away from the primary field of view. Comparing data from recent Murchison Widefield Array observations with simulations {\bf broken down by types of emission}, we identify diffuse emission near the horizon as a significant contributing factor, even on wide antenna spacings {\bf which are usually not sensitive to diffuse emission}. For signals entering through the primary field of view, compact emission dominates the foreground contamination. These two mechanisms imprint a characteristic {\it pitchfork} signature on the ``foreground wedge'' in Fourier space, {\bf which is found to be generic to wide--field measurements}. Based on these results, we propose that selective down--weighting of data based on antenna spacing and time {\bf can} mitigate foreground contamination substantially (up to a {\bf factor $\sim 100$} with negligible loss of sensitivity). {\bf A dish--shaped antenna yields the most desirable features from a foreground contamination viewpoint, relative to a dipole or a phased array}.

>>>>

\shorttitle{EoR Foregrounds in Fourier Space}
\shortauthors{Thyagarajan et~al.}

@@

%% \title{Detecting Epoch of Reionization in redshifted 21~cm: contamination in EoR window}
%% \title{Limits on the detection of the Epoch of Reionization from MWA observations of the redshifted 21~cm line}
\title{Foregrounds in Fourier Space for Redshifted 21~cm Observatories}

@@

Detection of 21~cm emission of H{\sc i} from the epoch of reionization, at redshifts $z>6$, is limited primarily by foreground emission. We investigate the signatures of wide--field measurements and an all--sky foreground model using the delay spectrum technique that maps the measurements to foreground object locations through signal delays between antenna pairs. We demonstrate interferometric measurements are inherently sensitive to all scales, including the largest angular scales, owing to the nature of wide--field measurements. These wide--field effects are generic to all observations but antenna shapes impact their amplitudes substantially. A dish--shaped antenna yields the most desirable features from a foreground contamination viewpoint, relative to a dipole or a phased array. Comparing data from recent Murchison Widefield Array observations, we demonstrate that the foreground signatures that have the largest impact on the H{\sc i} signal arise from power received far away from the primary field of view. We identify diffuse emission near the horizon as a significant contributing factor, even on wide antenna spacings. For signals entering through the primary field of view, compact emission dominates the foreground contamination. These two mechanisms imprint a characteristic {\it pitchfork} signature on the ``foreground wedge'' in Fourier space. Based on these results, we propose that selective down--weighting of data based on antenna spacing and time can mitigate foreground contamination substantially by a factor $\sim 100$ with negligible loss of sensitivity.
